---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/rstub/swephR.svg?branch=master)](https://travis-ci.org/rstub/swephR)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/rstub/swephR?branch=master&svg=true)](https://ci.appveyor.com/project/rstub/swephR)
[![Coverage status](https://codecov.io/gh/rstub/swephR/branch/master/graph/badge.svg)](https://codecov.io/github/rstub/swephR?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/swephR)](https://cran.r-project.org/package=swephR)
[![Downloads](http://cranlogs.r-pkg.org/badges/swephR?color=brightgreen)](http://www.r-pkg.org/pkg/swephR)

# swephR

The goal of swephR is to provide an R interface to the [Swiss
Ephemeris](https://www.astro.com/swisseph/). The Swiss Ephemeris is a
high precision ephemeris based upon the DE431 ephemerides from NASA's
JPL. It covers the time range 13201 BC to AD 17191.


## Installation

You can install the released version of swephR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("swephR")
```

Intermediate releases can also be obtained via [drat](https://cran.r-project.org/package=drat):

``` r
if (!requireNamespace("drat", quietly = TRUE)) install.packages("drat")
drat::addRepo("rstub")
install.packages("swephR")
```

This package uses the semi-analytic theory by Steve Moshier.  For
faster and more accurate calculations, the compressed Swiss Ephemeris
data is available in the 'swephRdata' package. To access this data
package, run

``` r
install.packages("swephRdata", repos = "https://rstub.github.io/drat/", type = "source")
```

The size of the 'swephRdata' package is approximately 115 MB. The user
can also use the original JPL DE431 data.

## Example

To compute the position of celestial body or star with SE (Swiss
Ephemeris), you do the following steps:

```{r}
library(swephR)
data(SE)
swe_version()
```

For a specific date, compute the Julian day number (in below example:
J2000.0, 1 January 2000 at 12:00 UT):

```{r}
year <- 2000
month <- 1
day <- 1
hour <- 12
jdut <- swe_julday(year, month, day, hour, SE$GREG_CAL)
jdut
```

Compute (using Moshier ephemeris) the positions (longitude, latitude,
distance, longitude speed and latitude speed) of a planet or other
celestial bodies (in below example: the Sun):

```{r}
ipl <- SE$SUN
iflag <- SE$FLG_MOSEPH + SE$FLG_SPEED
result <- swe_calc_ut(jdut, ipl, iflag)
result
```
or a fixed star (in below example: Sirius):

```{r}
starname = "sirius"
result <- swe_fixstar2_ut(starname, jdut, iflag)
result
```

The current R interface is modled after the C interface. It is
therefore often helpful to consult the [general
documentation](https://www.astro.com/swisseph/swisseph.htm) and
[programmer's
documentation](https://www.astro.com/swisseph/swephprg.htm) for the
Swiss Ephemeris.

## Feedback

All feedback (bug reports, security issues, feature requests, ...) should be provided as
[issues](https://github.com/rstub/swephR/issues).
