---
title: "swephR"
author: "Victor Reijs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{swephR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Some simple steps to do calculations
To compute a celestial body or point with SWISSEPH, you have to do the following steps (use swetest.c as an example). 

First load:
```{r}
library(swephR)
```
The details of the functions will be explained in the following chapters.

1. Set the directory path of the ephemeris files, e.g.:
```{r}
swe_set_ephe_path("C:\\sweph\\ephe")
```
1. From the birth date, compute the Julian day number:
```{r}
year <- 2000
month <- 1
day <- 1
hour <- 12
SE_GREG_CAL <- 1
jdut <- swe_julday(year, month, day, hour, SE_GREG_CAL)
jdut
```
1. Compute a planet or other bodies:
```{r}
planet_no <- 0
flag <- 4
result <- swe_calc_ut(jdut, planet_no, flag)
result
```
or a fixed star:
```{r}
starname = "sirius"
result <- swe_fixstar2_ut(starname, jdut, flag)
result
```

1.	At the end of your computations close all files and free memory calling 
```{r}
swe_close();
```
