---
title: "swephR"
author: "Victor Reijs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{swephR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Some simple steps to do calculations
To compute the position of celestial body or star with SE (Swiss Ephemeris), you do the following steps:


1. First load `swephR`:
```{r}
library(swephR)
```

2. Optionally set the directory path of the ephemeris files  (the format of the path depends on your OS), e.g.:
```{r, eval = FALSE}
swe_set_ephe_path("C:\\sweph\\ephe")
```

3. For a specific date, compute the Julian day number (in below example: J2000.0, 1 January 2000 at 12:00 UT):
```{r}
year <- 2000
month <- 1
day <- 1
hour <- 12
jdut <- swe_julday(year, month, day, hour, SE$GREG_CAL)
jdut
```

4. Compute (using Moshier ephemeris) the positions (longitude, latitude, distance, longitude speed and latitude speed) of a planet or other celestial bodies (in below example: the Sun):
```{r}
ipl <- SE$SUN
iflag <- SE$FLG_MOSEPH + SE$FLG_SPEED
result <- swe_calc_ut(jdut, ipl, iflag)
result
```
or a fixed star (in below example: Sirius):
```{r}
starname = "sirius"
result <- swe_fixstar2_ut(starname, jdut, iflag)
result
```

5. Determine the Julian day number of the Heliacal Rise of Sirius:
```{r}
options(digits=15)
result <- swe_heliacal_ut(jdut,c(0,50,10),c(1013.25,15,50,0.25),c(25,1,1,1,5,0.8),starname,
  SE$HELIACAL_RISING,SE$HELFLAG_HIGH_PRECISION+SE$FLG_MOSEPH)
result
```

6. Here is a miniature sample program described in Chapter 0 of the programmer's manual of SE ([see also](http://www.astro.com/swisseph/swephprg.htm#_Toc505244830)):
```{r}
  options(digits=6)
  swe_set_ephe_path(NULL)
  iflag = SE$FLG_SPEED + SE$FLG_MOSEPH
  {
    #get year
    jyear <- 2000
    #get month
    jmon <- 1
    #get day
    jday <- 1
    #get time
    jhour <- 12
    #determine julian day number (at 12:00 GMT)
    tjd_ut <- swe_julday(jyear, jmon, jday, jhour, SE$GREG_CAL)
    cat("Julian day number (UT) :", tjd_ut, "(",jyear,",",jmon,",",jday,"; proleptic Gregorian calendar)\n")
    cat("planet :",
        c("longitude", "latitude", "distance", "long. speed", "lat. speed"),
        "\n")
    cat("===========================================================\n")
    # loop over all planets
    for (p in SE$SUN:SE$OSCU_APOG) {
      # get the name of the planet p
      objectname = swe_get_planet_name(p)
        # do the coordinate calculation for this planet p
        i = swe_calc_ut(tjd_ut, p, iflag)
        if (i$return < 0) {
          cat("Error :", i$err, "(", objectname, ")\n")
        }
        else
        {
          # print data
          cat (objectname, ":", i$xx[0:5], "\n")
        }
    }
  }
```

7.	At the end of your computations close all files and free up memory:
```{r}
swe_close()
```
