---
title: "swephR"
author: "Victor Reijs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{swephR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Some simple steps to do calculations
To compute the position of celestial body or star with SE (Swiss Ephemeris), you do the following steps ([see also](http://www.astro.com/swisseph/swephprg.htm#_Toc505244830)):


1. First load `swephR` and constants used in swephR/SE:
```{r}
library(swephR)
SE<-SEConstants()
```

2. Optionaly set the directory path of the ephemeris files, e.g.:
```{r, eval = FALSE}
swe_set_ephe_path("C:\\sweph\\ephe")
```


3. For a specific date, compute the Julian day number (in below example: J2000.0, 1 January 2000 at 12:00 UT):
```{r}
year <- 2000
month <- 1
day <- 1
hour <- 12
jdut <- swe_julday(year, month, day, hour, SE$GREG_CAL)
jdut
```

4. Compute (using Moshier ephemeris) the positions (longitude, latitude, distance, longitude speed and latitude speed) of a planet or other celestial bodies (in below example: the Sun):
```{r}
ipl <- SE$SUN
iflag <- SE$FLG_MOSEPH + SE$FLG_SPEED
result <- swe_calc_ut(jdut, ipl, iflag)
result
```
or a fixed star (in below example: Sirius):
```{r}
starname = "sirius"
result <- swe_fixstar2_ut(starname, jdut, iflag)
result
```

5.	At the end of your computations close all files and free up memory:
```{r}
swe_close()
```
